---
title: "Chapter-5"
author: "Edgardo Rivera-Delgado"
format: html
editor: visual
---

# Chapter Notes

## Spending our Data

Data can be allocated for different modeling purposes such as: model building, model performance, parameter estimation, feature selection and so on. The two most common data splits are a training and a test set.

```{r}
library(tidymodels)

set.seed(501)

ames_split <- initial_split(ames, prop = 0.8)
ames_split
```

The data is split into train, test and finally the total is given.

Each of the splits can be extracted with its own function

```{r}
train <- training(ames_split)
test <- testing(ames_split)
```

The function initial_split() by default performs random sampling. If there's class imbalance in classification problems the argument strata can be provided specifying which column to use for stratification. For time series the function initial_time_split() should be used instead.

## Validation Set

Validation sets will be discussed in chapter 10.

## Multilevel Data

\*Independent experimental unit\* is the point where a datum is independent from another piece of datum.

## Other Considerations for a Data Budget

Keep test set in a separate data frame.

Subsample to reduce class inbalances and to better represent the test and training set.

After checking the performance of the data in the test set the modeler may want to refit the model using the entire data set.
